Technical Report

### 2018-06-18 fully-abstract-comp/technical-report.tex
Updated reasonability condition to have stk pointers in the reasonable words definition so it could be removed from the reasonable configuration definition.

\dominique{The below is an experimental reformulation of the reasonability requirement for the FTLR and full abstraction formulation.  All remarks welcome..
  The main change is that it now says that after a call, the post-return code is also expected to behave reasonably under reasonable assumptions. 
}
\dominique{TODO: better name than ``reasonable'' for all of this.}
Take a set of trusted addresses $\ta$ and sets of return pointer and closure seals $\gsigrets$ and $\sigcloss$.
We define that a word $w$ is reasonable up to $n$ steps in memory $\ms$ if $n=0$
or the following implications hold.
\begin{itemize}
\item If $w = \seal{\sigma_\baddr,\sigma_\eaddr,\_}$, then $[\sigma_\baddr,\sigma_\eaddr] \mathrel{\#} (\gsigrets \cup \gsigcloss)$
\item If $w = ((\perm,\_),\baddr,\eaddr,\_)$ and $\perm \neq 0$ and $\gsigrets \neq \emptyset$, then $[\baddr,\eaddr] \# \dom(\ta)$
\item If $w = \sealed{\sigma,\vsc}$ and $\sigma \not\in (\gsigrets\cup \gsigcloss)$ then $\vsc$ is reasonable up to $n - 1$ steps.
\item If $w = ((\perm,\_),\baddr,\eaddr,\_)$ and $\perm \in \readAllowed{}$ and $n > 0$, then $\ms(\aaddr)$ is reasonable up to $n - 1$ steps for all $\aaddr \in ([\baddr,\eaddr] \setminus \ta)$
\end{itemize}

@@

We say that an executable capability $c = ((\perm,\normal),\baddr,\eaddr,\aaddr)$ behaves reasonably up to $n$ steps if for any $\Phi$ such that
  \begin{itemize}
  \item $\Phi.\reg(\pcreg) = c$
  \item $\Phi.\reg(r)$ is reasonable up to $n$ steps in memory $\Phi.\mem$ for all $r \not\in \{\pcreg\}$
  \item $\Phi.\ms_\stk$ is reasonable up to $n-1$ steps in memory $\Phi.\mem$ for all $a$
  \item $\Phi.\mem$, $\Phi.\ms_\stk$ and $\Phi.\stk$ are all disjoint
  \end{itemize}
  We have that $\Phi$ is reasonable.

@@

    TODO
  \end{itemize}
\end{proof}

\begin{lemma}
  If
  \begin{itemize}
  \item $\npair{(\reg_S,\_)} \in \lrr(W_w)$
  \item $\memSat{\ms_S,\stk,\ms_\stk,\_}{W_M}$
  \item $W_w \oplus W_M$ is defined
  \item $\pwheap[W_w](r) \nequal \codereg{\sigrets,\sigcloss,\code,(\ta,\stkb)}$
  \item $\dom(\code) \subseteq \ta$
  \item $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$
  \end{itemize}
  then, with respect to $\code,\ta,\gsigrets,\gsigcloss$,
  \begin{itemize}
  \item $\Phi.\reg(r)$ is reasonable up to $n$ steps in memory $\Phi.\mem$ for all $r \not\in \{\pcreg\}$
  \item $\Phi.\ms_\stk$ is reasonable up to $n-1$ steps in memory $\Phi.\mem$ for all $a$
  \item $\Phi.\mem$, $\Phi.\ms_\stk$ and $\Phi.\stk$ are all disjoint
  \end{itemize}
\end{lemma}
\begin{proof}
  We prove the three results separately:
  \begin{itemize}
  \item $\Phi.\reg(r)$ is reasonable up to $n$ steps in memory $\Phi.\mem$ for all $r \not\in \{\pcreg\}$:

@@

  \item $\Phi.\ms_\stk$ is reasonable up to $n-1$ steps in memory $\Phi.\mem$ for all $a$:

    TODO
  \item $\Phi.\mem$, $\Phi.\ms_\stk$ and $\Phi.\stk$ are all disjoint:

>>>>

\dominique{The below is an experimental reformulation of the reasonability requirement for the FTLR and full abstraction formulation.  All remarks welcome..
  The main change is that it now says that after a call, the post-return code is also expected to behave reasonably under reasonable assumptions. 
}
\dominique{TODO: better name than ``reasonable'' for all of this.}
Take a set of trusted addresses $\ta$ and sets of return pointer and closure seals $\gsigrets$ and $\sigcloss$.
We define that a word $w$ is reasonable up to $n$ steps in memory $\ms$ and
free stack $\ms_\stk$ if $n=0$
or the following implications hold.
\begin{itemize}
\item If $w = \seal{\sigma_\baddr,\sigma_\eaddr,\_}$, then $[\sigma_\baddr,\sigma_\eaddr] \mathrel{\#} (\gsigrets \cup \gsigcloss)$
\item If $w = ((\perm,\_),\baddr,\eaddr,\_)$ and $\perm \neq 0$ and $\gsigrets \neq \emptyset$, then $[\baddr,\eaddr] \# \dom(\ta)$
\item If $w = \sealed{\sigma,\vsc}$ and $\sigma \not\in (\gsigrets\cup \gsigcloss)$ then $\vsc$ is reasonable up to $n - 1$ steps.
\item If $w = ((\perm,\_),\baddr,\eaddr,\_)$ and $\perm \in \readAllowed{}$ and $n > 0$, then $\ms(\aaddr)$ is reasonable up to $n - 1$ steps for all $\aaddr \in ([\baddr,\eaddr] \setminus \ta)$
\item If $w = \stkptr{\perm,\baddr,\eaddr,\_}$ and $\perm \in \readAllowed{}$ and $n > 0$, then $\ms_\stk(\aaddr)$ is reasonable up to $n - 1$ steps for all $\aaddr \in [\baddr,\eaddr]$
\end{itemize}

@@

We say that an executable capability $c = ((\perm,\normal),\baddr,\eaddr,\aaddr)$ behaves reasonably up to $n$ steps if for any $\Phi$ such that
  \begin{itemize}
  \item $\Phi.\reg(\pcreg) = c$
  \item $\Phi.\reg(r)$ is reasonable up to $n$ steps in memory $\Phi.\mem$ and free stack $\Phi.\ms_\stk$for all $r \not\in \{\pcreg\}$
  \item $\Phi.\mem$, $\Phi.\ms_\stk$ and $\Phi.\stk$ are all disjoint
  \end{itemize}
  We have that $\Phi$ is reasonable.

@@

  \item If $w = \stkptr{\perm,\baddr,\eaddr,\_}$ and $\perm \in \readAllowed{}$ and $n > 0$, then $\ms_\stk(\aaddr)$ is reasonable up to $n - 1$ steps for all $\aaddr \in [\baddr,\eaddr]$:

  \end{itemize}
\end{proof}

\begin{lemma}
  If
  \begin{itemize}
  \item $\npair{(\reg_S,\_)} \in \lrr(W_w)$
  \item $\memSat{\ms_S,\stk,\ms_\stk,\_}{W_M}$
  \item $W_w \oplus W_M$ is defined
  \item $\pwheap[W_w](r) \nequal \codereg{\sigrets,\sigcloss,\code,(\ta,\stkb)}$
  \item $\dom(\code) \subseteq \ta$
  \item $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$
  \end{itemize}
  then, with respect to $\code,\ta,\gsigrets,\gsigcloss$,
  \begin{itemize}
  \item $\Phi.\reg(r)$ is reasonable up to $n$ steps in memory $\Phi.\mem$ and free stack $\Phi.\ms_\stk$for all $r \not\in \{\pcreg\}$
  \item $\Phi.\mem$, $\Phi.\ms_\stk$ and $\Phi.\stk$ are all disjoint
  \end{itemize}
\end{lemma}
\begin{proof}
  We prove the three results separately:
  \begin{itemize}
  \item $\Phi.\reg(r)$ is reasonable up to $n$ steps in memory $\Phi.\mem$ for all $r \not\in \{\pcreg\}$:

@@

  \item $\Phi.\mem$, $\Phi.\ms_\stk$ and $\Phi.\stk$ are all disjoint:
